cardinalR: Generating interesting high-dimensional data structures

### 2025-09-23 paper-cardinalR.Rmd
Updated Figure width and height

```{r branch-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `expbranches` (a1-a3), `linearbranches` (b1-b3), `curvybranches` (c1-c3), `orglinearbranches` (d1-d3), `orgcurvybranches` (e1-e3) data.", fig.width=15, fig.height=25}

@@

```{r cone-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `cone` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r cube-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gridcube` (a1-a3), `unifcube` (b1-b3), and `cubehole` (c1-c3) data.", fig.width=15, fig.height=15}

@@

```{r gau-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gau` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r linear-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `linear` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r mobius-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `mobius` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r poly-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `quadratic` (a1-a3) and `cubic` (b1-b3) data.", fig.width=15, fig.height=10}

@@

```{r pyr-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data.", fig.width=15, fig.height=20}

@@

```{r scurve-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `scurve` (a1-a3) and `scurvehole` (b1-b3) data.", fig.width=15, fig.height=10}

@@

```{r sphere-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), `unifsphere` (c1-c3), `gridedsphere` (d1-d3), `clusteredspheres` (e1-e3), and `hemisphere` (f1-f3) data.", fig.width=15, fig.height=35, out.width="80%", fig.align='center'}

@@

```{r swissroll-proj, eval=knitr::is_latex_output(), fig.pos="H", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `swissroll` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r triginometric-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `crescent` (a1-a3), `curvycylinder` (b1-b3), `sphericalspiral` (c1-c3), `helicalspiral` (d1-d3), `conicspiral` (e1-e3), and `nonlinear` (f1-f3) data.", fig.width=15, fig.height=35, out.width="80%", fig.align='center'}

@@

```{r trefoil-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `trefoil4d` (a1-a3) and `trefoil3d` (b1-b3) data.", fig.width=15, fig.height=10}

@@

```{r highd-proj, eval=knitr::is_latex_output(), fig.pos='H', fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green."}
#| fig-width: 15
#| fig-height: 5

>>>>

```{r branch-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `expbranches` (a1-a3), `linearbranches` (b1-b3), `curvybranches` (c1-c3), `orglinearbranches` (d1-d3), `orgcurvybranches` (e1-e3) data.", fig.width=12, fig.height=20}

@@

```{r cone-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `cone` data."}
#| fig-width: 12
#| fig-height: 4

@@

```{r cube-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gridcube` (a1-a3), `unifcube` (b1-b3), and `cubehole` (c1-c3) data.", fig.width=12, fig.height=12}

@@

```{r gau-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gau` data."}
#| fig-width: 12
#| fig-height: 4

@@

```{r linear-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `linear` data."}
#| fig-width: 12
#| fig-height: 4

@@

```{r mobius-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `mobius` data."}
#| fig-width: 12
#| fig-height: 4

@@

```{r poly-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `quadratic` (a1-a3) and `cubic` (b1-b3) data.", fig.width=12, fig.height=8}

@@

```{r pyr-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data.", fig.width=12, fig.height=16}

@@

```{r scurve-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `scurve` (a1-a3) and `scurvehole` (b1-b3) data.", fig.width=12, fig.height=8}

@@

```{r sphere-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), `unifsphere` (c1-c3), `gridedsphere` (d1-d3), `clusteredspheres` (e1-e3), and `hemisphere` (f1-f3) data.", fig.width=12, fig.height=28, out.width="80%", fig.align='center'}

@@

```{r swissroll-proj, eval=knitr::is_latex_output(), fig.pos="H", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `swissroll` data."}
#| fig-width: 12
#| fig-height: 4

@@

```{r triginometric-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `crescent` (a1-a3), `curvycylinder` (b1-b3), `sphericalspiral` (c1-c3), `helicalspiral` (d1-d3), `conicspiral` (e1-e3), and `nonlinear` (f1-f3) data.", fig.width=12, fig.height=28, out.width="80%", fig.align='center'}

@@

```{r trefoil-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `trefoil4d` (a1-a3) and `trefoil3d` (b1-b3) data.", fig.width=12, fig.height=8}

@@

```{r highd-proj, eval=knitr::is_latex_output(), fig.pos='H', fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green."}
#| fig-width: 12
#| fig-height: 4
